---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


Orsi fronts in Spatial form
---------------------------

The "Orsi fronts" are a commonly used climatological map of Southern Ocean frontal distributions, published on the
[Southern Ocean Atlas Database Page](http://woceatlas.tamu.edu/Sites/html/atlas/SOA_DATABASE_DOWNLOAD.html) after Orsi et al. (1995). 


The data is provided in this package as a built-in data set. The object `orsifronts` is a 'SpatialLinesDataFrame' object, as defined in the 'sp' package. This is a "GIS vector" layer where complex line geometry objects are linked to data in a table form. 

```{r}
library(orsifronts)
cols <- hcl(seq(0, 240, length = nrow(orsifronts)), c = 50)
plot(orsifronts, col = cols, lwd = 2)

```

There are `nrow(orsifronts)` line objects, with some simple names and codes. 

```{r}
as.data.frame(orsifronts)
plot(orsifronts, xlim = c(130, 18), col = cols, asp = 1/cos(60 * pi / 180), lwd = 4)
legend("topleft", sprintf("%s (%s)", orsifronts$front, orsifronts$name),  col = cols, lwd = 4, cex = 0.8)
degAxis(1)
degAxis(2)
box()
```



# References

Orsi, A. H., T. Whitworth III and W. D. Nowlin, Jr. (1995). On the meridional extent and fronts of the Antarctic Circumpolar Current, Deep-Sea Research I, 42, 641-673.

