---
title: "Orsi Fronts for R"
author: "Michael Sumner"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{orsifronts}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Orsi fronts for R
---------------------------

The "Orsi fronts" are a commonly used climatological map of Southern Ocean frontal distributions, published on the
[Southern Ocean Atlas Database Page](http://woceatlas.tamu.edu/Sites/html/atlas/SOA_DATABASE_DOWNLOAD.html) after Orsi et al. (1995). 


The data is provided in this package as a built-in data set. The object `orsifronts` is a 'SpatialLinesDataFrame' object, as defined in the 'sp' package. (A 'SpatialLinesDataFrame' is a "GIS vector" layer where complex line geometry objects are linked to simple attribute data in a table form, and it behaves like a 'data.frame'). 

```{r}
library(orsifronts)
cols <- hcl(seq(0, 240, length = nrow(orsifronts)), c = 50)
plot(orsifronts, col = cols, lwd = 2)
degAxis(1)
degAxis(2)
box()
```

There are `r nrow(orsifronts)` line objects, with some simple names and codes. 

```{r}
as.data.frame(orsifronts)
plot(orsifronts, xlim = c(60, 180), col = cols, asp = 1/cos(55 * pi / 180), lwd = 4)
legend("topleft", sprintf("%s (%s)", orsifronts$front, orsifronts$name),  col = cols, lwd = 4, cex = 0.8, bty = "n")
degAxis(1)
degAxis(2)
box()
```



# References

Orsi, A. H., T. Whitworth III and W. D. Nowlin, Jr. (1995). On the meridional extent and fronts of the Antarctic Circumpolar Current, Deep-Sea Research I, 42, 641-673.

